%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : Adam Pribyl, Tomas Polasek (template)
% Description : First exercise in the Introduction to Game Development course.
%   It deals with an analysis of a selected title from the point of its genre, 
%   style, and mechanics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\newcommand{\ph}[1]{\textit{[#1]}}

\title{%
Analysis of Mechanics%
}
\author{%
Adam Přibyl (xpribya00)%
}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} \ph{Alan Wake 2}

\item[] \textbf{Released:} \ph{2023}

\item[] \textbf{Author:} \ph{Remedy Entertainment / Epic Games Publishing}

\item[] \textbf{Primary Genre:} \ph{Adventure}

\item[] \textbf{Secondary Genre:} \ph{Survival horror, Story}

\item[] \textbf{Style:} \ph{Realistic, Supernatural}

\end{itemize}

}

\section*{\centering Analysis}

\subsection*{Adventure}
Apart from the combat, main gameplay of the game is puzzle solving. The player assumes role of a hero (two heroes in this case), the game is highly narrative. All of these things mentioned is a classic example of adventure game. The Survival Horror subgenre expands the Adventure genre.

\subsection*{Survival Horror}
The game is played like a traditional survival horror game. The game contains classic survival horror features like: 
\begin{enumerate}
\item Ammo scarcity
\item Inventory management
\item Dangerous enemies
\item Environmental puzzles
\end{enumerate}

Some mechanics that set Alan Wake 2 apart from other survival horror games like Resident Evil and Silent Hill series is a clever way of working with light and the environment. The player uses his flashlight to weaken the enemies which fits perfectly with the dark and mysterious atmosphere of the game and also supports the exact and methodical combat of survival horror games. The horror aspect of \textbf{survival horror} is present throughout the game, and some parts of the game even contain some form of jumpscares. The game is a highly story-driven \textbf{ thriller} experience. The game perfectly creates a heavy and nerve-wracking atmosphere. 

\subsection*{Story}
As mentioned above, the game is heavily story driven, which works with the adventure genre.
The game contains almost 5 hours of cutscenes, so its almost 25 \% of the 20 hour game.
The player is instantly drawn into this dark thriller murder mystery story. The story as well as gameplay is divided into 2 parts, each viewed by separate character. The player takes control of a federal agent investigating a case and a character trapped in this paranormal mystery (The character is Alan Wake - a writer that is trapped in his own dark story). Good story is an essential part of every adventure game. The story was written by the genious writer Sam Lake.

\subsection*{The Style}
\subsubsection*{Realism}
The realistic style of the game makes it feel even more like a movie. It pulls you in and makes you feel like you are there, it makes you live out the \textbf{Adventure}. The realistic side of gameplay is visible in for example the way the character moves, reloads and how much stamina Saga and Alan have, making the game more tense in some moments, the player really feels the weight of every move. The realistic style makes complete sense to be here, the game might as well be a movie (there is already one announced, so it will be).

\subsubsection*{Supernatural}
Supernatural style expands whats possible in the world and that is used greatly for puzzles in the gameplay of the game. The supernatulity of the game can also be viewed in the flashlight mechanic that was mentioned before. The supernatural make complete sense in the context of the story.


\end{document}
